### 2023-10-20 records/manuscript_2023.tex
improve code and polish Fig 3 and 3S1

\textbf{Figure 3:} $100$ trials, each simulated for $5000$ time steps. In a trail, $10$ constant values were drawn from a normal distribution (each $500$ time steps long). The variance of this distribution was $0$ (C, F)  and $5.3$ XXX (D). In each trial, the stimulus mean was drawn from an uniform distribution $U(a, b)$ (C: $U(1,9)$, D: $U(5,5)$). In F, $U$ was parameterized such that the trail variability was $3$.\\

@@

\textbf{Figure 3 Supplementary Fig. 1:}  $120$ trials, each simulated for $5000$ time steps. In a trail, $10$ constant values were drawn from a normal distribution $N(\mu_\mathrm{in}, \sigma_\mathrm{in})$, each $500$ time steps long. In each trial, the stimulus mean was drawn from an uniform distribution $U(a, b)$. Switch of input statistics occurs after 60 trails. State 1: stimulus $\in N(\mu_\mathrm{in}, 0)$ with $\mu_\mathrm{in} \in U(5,5)$, State 2:  stimulus $\in N(\mu_\mathrm{in}, 3)$ with $\mu_\mathrm{in} \in U(5,5)$, State 3: stimulus $\in N(\mu_\mathrm{in}, 3)$ with $\mu_\mathrm{in} \in U(0,10)$, State 4: stimulus $\in N(\mu_\mathrm{in}, 0)$ with $\mu_\mathrm{in} \in U(0,10)$.\\

>>>>

\textbf{Figure 3:} $100$ trials, each simulated for $5000$ time steps. In a trail, $10$ constant values were drawn from a normal distribution (each $500$ time steps long). The variance of this distribution was $0$ (C, F)  and $5$ (D). In each trial, the stimulus mean was drawn from an uniform distribution $U(a, b)$ (C: $U(1,9)$, D: $U(5,5)$). In F, $U(a,b)$ was parameterized such that the trail variability was $3$.\\

@@

\textbf{Figure 3 Supplementary Fig. 1:}  $100$ trials, each simulated for $5000$ time steps. In a trail, $10$ constant values were drawn from a normal distribution $N(\mu_\mathrm{in}, \sigma_\mathrm{in})$, each $500$ time steps long. In each trial, the stimulus mean was drawn from an uniform distribution $U(a, b)$. Switch of input statistics occurs after 50 trails. State 1: stimulus $\in N(\mu_\mathrm{in}, 0)$ with $\mu_\mathrm{in} \in U(5,5)$, State 2:  stimulus $\in N(\mu_\mathrm{in}, 3)$ with $\mu_\mathrm{in} \in U(5,5)$, State 3: stimulus $\in N(\mu_\mathrm{in}, 3)$ with $\mu_\mathrm{in} \in U(0,10)$, State 4: stimulus $\in N(\mu_\mathrm{in}, 0)$ with $\mu_\mathrm{in} \in U(0,10)$.\\
